Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-09-06 manuscript/manuscript.tex
fix notation
updates notations. removes redundant ITS equation.

\begin{equation}
\label{eq:spectral_left}
\phi_i  T(\tau) = \lambda_i \phi_i,
\end{equation}

@@

\begin{equation}
\label{eq:spectral_right}
T(\tau)\psi_i = \lambda_i \psi_i,
\end{equation}

@@

The highest eigenvalue, $\lambda_1$, is unique and is equal to $1$, and its corresponding left eigenvector $\phi_1$ corresponds to the stationary distribution, $\pi$.
From the relationship between the left and right eigevenctors (eq.~\ref{eq:left-right-eigenvalue-relation}) we see that the right eigenvector $\psi_1$ is a vector consisting of~$1$'s.

The subsequent eigenvalues $\lambda_{i>1}$ are real with absolute values less than~$1$ and are related to the \emph{characteristic} or \emph{implied} time-scales of dynamical processes within the system, through
\begin{equation}
	\label{eq:timescales}
	t_i \equiv -\frac{\tau}{\log|\lambda_i|}.
\end{equation}

>>>>

\begin{equation}
\label{eq:spectral_left}
\phi_i^\top  T(\tau) = \lambda_i(\tau) \phi_i^\top,
\end{equation}

@@

\begin{equation}
\label{eq:spectral_right}
T(\tau)\psi_i = \lambda_i(\tau) \psi_i,
\end{equation}

@@

The highest eigenvalue, $\lambda_1(\tau)$, is unique and is equal to $1$, and its corresponding left eigenvector $\phi_1$ corresponds to the stationary distribution, $\pi$.
From the relationship between the left and right eigenvectors (eq.~\ref{eq:left-right-eigenvalue-relation}) we see that the right eigenvector $\psi_1$ is a vector consisting of~$1$'s.

The subsequent eigenvalues $\lambda_{i>1}(\tau)$ are real with absolute values less than~$1$ and are related to the \emph{characteristic} or \emph{implied} time-scales of dynamical processes within the system~\ref{eq:its}.
